\section*{Glossary}
\label{sec:Glossary}

\begin{itemize}
\item \textbf{ASCII}: Abbreviation of American Standard Code for Information Interchange. ASCII is a character encoding that represents text in computers, telecommunications equipment\textbf{}, and other devices.
\item \textbf{Class}: A class is the main structure of the oriented-object programming and is responsible for implementing the behaviour and also values for the state of an object.
\item \textbf{Utils}: Utils is a FENCE class that contains useful public methods used by many other classes of the Framework.
\item \textbf{Cronjob}: Cronjobs are commands or scripts that run periodically at fixed times.
\item \textbf{Egroup}: E-groups are multi-purpose groups formed by CERN members which can be used as email address.
\item \textbf{authorlist}: It is the easy-wording to say and write "author list". 
\item \textbf{EOS file system}: EOS is a software solution that aims to provide fast and reliable multi-PetaByte disk-only storage technology for both LHC and non-LHC use-cases at CERN.
\item \textbf{Git}: Git is a Distributed Version Control System and its aim is to manage software development projects and its files that changes over time. It stores this information in a repository.
\item \textbf{Gitlab}: Gitlab is a web-based Git repository.
\item Branch: Branches are pointers to a snapshot changes on Git.
\item \textbf{Svn}: Apache Subversion (or SVN) was one of the most popular Version Control Systems before 2010 and it is nowadays being substituted by more modern ones as Git.
\item \textbf{JSON}: Abbreviation of JavaScript Object Notation. JSON is a lightweight format for storing and transporting data.
\item \textbf{XML}: Abbreviation of eXtensible Markup Language. XML it is a markup language also designed for storing and transporting data.
\item \textbf{PHP}: PHP is a programming language commonly used for web development.
\item \textbf{PROLOG}: PROLOG is a programming language commonly used by artificial intelligence applications.
\item \textbf{Python}: Python is a multi-purpose, interpreted, object-oriented and high-level programming language.
\end{itemize}


